Magnetized Polish doughnuts revisited

### 2017-03-14 paper.tex
Tables 1 & 2 updated. Figure 1 updated.

\begin{figure*}[t]
\centering
\includegraphics[scale=0.16]{figures/fig1a.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.16]{figures/fig1b.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.16]{figures/fig1c.pdf}
\caption{\sg{update figures.}Comparison with Komissarov's solution for a constant angular momentum model. The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
           \label{komissarov}%
 \end{figure*}

@@

\begin{table}
\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}
$. Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$. \sg{Update table.}}             
\label{table:1}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
\hline           
A1 & $0.0$ & $0.0$ &  $7.15$  & $8.14$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.8$\\ 
A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.58$\\ 
A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.68$\\ 
A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
 \hline 
B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.54$\\ 
B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
 \hline 
C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
\hline      
\end{tabular}
\end{table}

\begin{table}
\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1
$. Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$. \sg{Update table.}}             
\label{table:3}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
\hline           
A1 & $0.0$ & $0.0$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.8$\\ 
A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.58$\\ 
A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.68$\\ 
A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
 \hline 
B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.54$\\ 
B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
 \hline 
C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
\hline      
\end{tabular}
\end{table}

\begin{table}
\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}
$. Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}             
\label{table:3}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
\hline           
A1 & $0.0$ & $0.0$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $12$\\ 
A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.6$\\ 
A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.7$\\ 
A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
 \hline 
B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.4$\\ 
B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.5$\\ 
B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-0.129$ & $1.73$ & $4.5$\\ 
B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
 \hline 
C1 & $0.0$ & $0.0$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.5$\\ 
C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.3$\\ 
C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.3$\\ 
C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
\hline      
\end{tabular}
\end{table}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[scale=0.16]{figures/fig1a.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.16]{figures/fig1b.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.16]{figures/fig1c.pdf}
\caption{Comparison with Komissarov's solution for a constant angular momentum model. The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
           \label{komissarov}%
 \end{figure*}

@@

\begin{table}
\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}
$. Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}             
\label{table:1}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W (\times 10^{-2})$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
\hline           
A1 & $0.0$ & $0.0$ & $7.15$ &  $8.14$  & $-6.35$ & $2.91$ & -- \\ 
A2 & $0.5$ & $0.5$ & $7.15$ &  $7.65$  & $-2.27$ & $3.20$ & $11.8$\\ 
A3 & $0.9$ & $0.9$ & $7.15$ &  $7.45$  & $-0.30$ & $3.70$ &  $9.58$\\ 
A4 & $0.0$ & $0.9$ & $7.15$ &  $8.32$  & $-6.35$ & $2.91$ & $9.68$\\ 
A5 & $0.9$ & $0.0$ & $7.15$ &  $7.28$  & $-0.30$ & $3.70$ & --\\ 
 \hline 
B1 & $0.0$ & $0.0$ & $3.59$ &  $3.98$  & $-12.9$ & $1.73$ & -- \\ 
B2 & $0.5$ & $0.5$ & $3.59$ &  $3.83$  & $-4.32$ & $1.86$ & $5.35$\\ 
B3 & $0.9$ & $0.9$ & $3.59$ &  $3.73$  & $-0.54$ & $2.08$ & $4.52$\\ 
B4 & $0.0$ & $0.9$ & $3.59$ &  $3.85$  & $-12.9$ & $1.73$ & $4.54$\\ 
B5 & $0.9$ & $0.0$ & $3.59$ &  $3.81$  & $-0.54$ & $2.08$ & -- \\  
 \hline 
C1 & $0.0$ & $0.0$ & $1.98$ &  $2.28$  & $-24.6$ & $1.21$ & -- \\ 
C2 & $0.5$ & $0.5$ & $1.98$ &  $2.09$  & $-7.34$ & $1.26$ & $2.50$\\ 
C3 & $0.9$ & $0.9$ & $1.98$ &  $2.04$  & $-0.85$ & $1.35$ & $2.25$\\ 
C4 & $0.0$ & $0.9$ & $1.98$ &  $2.10$  & $-24.6$ & $1.21$ & $2.26$\\ 
C5 & $0.9$ & $0.0$ & $1.98$ &  $2.08$  & $-0.85$ & $1.35$ & --\\ 
\hline      
\end{tabular}
\end{table}

\begin{table}
\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 1
$. Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}             
\label{table:3}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W (\times 10^{-2})$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
\hline           
A1 & $0.0$ & $0.0$ & $6.00$ &  $6.49$  & $-6.35$ & $2.91$ & -- \\ 
A2 & $0.5$ & $0.5$ & $6.25$ &  $6.66$  & $-2.27$ & $3.20$ & $11.8$\\ 
A3 & $0.9$ & $0.9$ & $6.50$ &  $6.80$  & $-0.30$ & $3.70$ &  $9.58$\\ 
A4 & $0.0$ & $0.9$ & $6.00$ &  $6.49$  & $-6.35$ & $2.91$ & $9.68$\\ 
A5 & $0.9$ & $0.0$ & $6.50$ &  $6.80$  & $-0.30$ & $3.70$ & --\\ 
 \hline 
B1 & $0.0$ & $0.0$ & $3.02$ &  $3.26$  & $-12.9$ & $1.73$ & -- \\ 
B2 & $0.5$ & $0.5$ & $3.16$ &  $3.35$  & $-4.32$ & $1.86$ & $5.35$\\
B3 & $0.9$ & $0.9$ & $3.29$ &  $3.43$  & $-0.54$ & $2.08$ & $4.52$\\ 
B4 & $0.0$ & $0.9$ & $3.02$ &  $3.26$  & $-12.9$ & $1.73$ & $4.54$\\  
B5 & $0.9$ & $0.0$ & $3.29$ &  $3.43$  & $-0.54$ & $2.08$ & -- \\ 
 \hline 
C1 & $0.0$ & $0.0$ & $1.68$ &  $1.80$  & $-0.246$ & $1.21$ & -- \\ 
C2 & $0.5$ & $0.5$ & $1.77$ &  $1.86$  & $-7.34$ & $1.26$ & $2.50$\\  
C3 & $0.9$ & $0.9$ & $1.84$ &  $1.91$  & $-0.85$ & $1.35$ & $2.25$\\ 
C4 & $0.0$ & $0.9$ & $1.68$ &  $1.80$  & $-24.6$ & $1.21$ & $2.26$\\ 
C5 & $0.9$ & $0.0$ & $1.84$ &  $1.91$  & $-0.85$ & $1.35$ & --\\ 
\hline      
\end{tabular}
\end{table}

\begin{table}
\caption{List of models for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}
$. Form left to right the columns report: the model name (with A, B and C standing for black hole spin $a = 0.5$, $0.9$ and $0.99$ respectively), the parameters of the angular momentum distribution $\beta$ and $\gamma$, , the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and $r_{\mathrm{out}}$.}             
\label{table:3}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 & $\beta$ & $\gamma$ & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W (\times 10^{-2})$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
\hline           
A1 & $0.0$ & $0.0$ & $5.11$ &  $5.51$  & $-6.35$ & $2.91$ & -- \\ 
A2 & $0.5$ & $0.5$ & $5.55$ &  $5.80$  & $-2.27$ & $3.20$ & $11.8$\\ 
A3 & $0.9$ & $0.9$ & $5.95$ &  $6.15$  & $-0.30$ & $3.70$ &  $9.58$\\ 
A4 & $0.0$ & $0.9$ & $5.21$ &  $5.51$  & $-6.35$ & $2.91$ & $9.68$\\  
A5 & $0.9$ & $0.0$ & $5.90$ &  $6.10$  & $-0.30$ & $3.70$ & --\\
 \hline 
B1 & $0.0$ & $0.0$ & $2.53$ &  $2.73$  & $-12.9$ & $1.73$ & -- \\ 
B2 & $0.5$ & $0.5$ & $2.81$ &  $2.91$  & $-4.32$ & $1.86$ & $5.35$\\
B3 & $0.9$ & $0.9$ & $3.03$ &  $3.13$  & $-0.54$ & $2.08$ & $4.52$\\  
B4 & $0.0$ & $0.9$ & $2.65$ &  $2.80$  & $-12.9$ & $1.73$ & $4.54$\\ 
B5 & $0.9$ & $0.0$ & $3.03$ &  $3.13$  & $-0.54$ & $2.08$ & -- \\  
 \hline 
C1 & $0.0$ & $0.0$ & $1.46$ &  $1.51$  & $-24.6$ & $1.21$ & -- \\ 
C2 & $0.5$ & $0.5$ & $1.56$ &  $1.61$  & $-7.34$ & $1.26$ & $2.50$\\ 
C3 & $0.9$ & $0.9$ & $1.70$ &  $1.75$  & $-0.85$ & $1.35$ & $2.25$\\ 
C4 & $0.0$ & $0.9$ & $1.50$ &  $1.57$  & $-24.6$ & $1.21$ & $2.26$\\ 
C5 & $0.9$ & $0.0$ & $1.72$ &  $1.77$  & $-0.85$ & $1.35$ & --\\ 
\hline      
\end{tabular}
\end{table}
